19Q1

### 2019-03-25 19Q1.Rmd
update poz to use unique CCLs as rows

# Accout for cell line aliases and missing histologies
auc_unmatched_na_histologies <- read.delim("./data_munging/pozdeyev2016/auc_unmatched_na_histologies.csv", sep = ",", row.names = 1)
auc_unmatched_na_histologies$accession_id <- NULL
auc_unmatched_na_histologies$Notes <- NULL
auc_unmatched_na_histologies$Histology <- ifelse(auc_unmatched_na_histologies$Histology == "", NA, as.character(auc_unmatched_na_histologies$Histology))
auc_unmatched_na_histologies$CCLE_ccl_name <- ifelse(auc_unmatched_na_histologies$CCLE_ccl_name  == "", NA, as.character(auc_unmatched_na_histologies$CCLE_ccl_name ))
auc_unmatched_na_histologies$Broad_ID <- ifelse(auc_unmatched_na_histologies$Broad_ID == "", NA, as.character(auc_unmatched_na_histologies$Broad_ID))

@@

```{r}
ccle_poz <- read.delim("./data_munging/pozdeyev2016/CCLE_drug_response_metrics.csv.gz", sep = ",")
ccle_poz <- merge(ccl_histologies, ccle_poz, by = "Cell_line", all.y = TRUE)
# ccle_test <- merge(select(ccle_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "CCLE"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)

ctrp_poz <- read.delim("./../htscreens_giant_files/pozdeyev2016/CTRP_drug_response_metrics.csv.gz", sep = ",")
ctrp_poz <- merge(ccl_histologies, ctrp_poz, by = "Cell_line", all.y = TRUE)
# ctrp_test <- merge(select(ctrp_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "CTRP"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)

gdsc_poz <- read.delim("./data_munging/pozdeyev2016/GDSC_drug_response_metrics.csv.gz", sep = ",")
gdsc_poz <- merge(ccl_histologies, gdsc_poz, by = "Cell_line", all.y = TRUE)
# gdsc_test <- merge(select(gdsc_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "GDSC"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)

auc_unmatched <- bind_rows(ccle_poz, ctrp_poz, gdsc_poz)
auc_unmatched$AUC_EC50 <- as.numeric(as.character(auc_unmatched$AUC_EC50))
auc_unmatched$AUC_IC50 <- as.numeric(as.character(auc_unmatched$AUC_IC50))
auc_unmatched$sample_ID <- with(auc_unmatched, paste(Database, Cell_line, Histology, sep = "_"))
num_auc_per_db_unmatched <- auc_unmatched %>% count(Database)

@@

# Create merged dataset with sample_ids in the rows and drugs across the columns
auc_unmatched_wide <- dcast(auc_unmatched, Database + Cell_line + Histology + sample_ID + CCLE_ccl_name + Broad_ID ~ Drug_name, value.var = "AUC_IC50", fun.aggregate = mean, fill = 1000000)
auc_unmatched_wide[, 7:ncol(auc_unmatched_wide)] <- auc_unmatched_wide[, 7:ncol(auc_unmatched_wide)] %>% replace_with_na_all(condition = ~.x == 1000000)
# write.csv.gz(auc_unmatched_wide, file = "./data_munging/pozdeyev2016/merged_auc_v20190319.2.csv.gz", row.names = FALSE, na = "NA")
```

@@

Plots:
```{r}
futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
venn_all_ccl_unmatched_pozdeyev <- venn.diagram(list("CCLE" = unique(ccle_poz$Cell_line), "CTRP" = unique(ctrp_poz$Cell_line), "GDSC" = unique(gdsc_poz$Cell_line)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
# png("./gcn_denise/pozdeyev_unmatched/pozdeyev_venn_all_ccl_unmatched.png", res = 500, units = "in", width = 6, height = 6)
# grid.newpage()
# grid.draw(venn_all_ccl_unmatched_pozdeyev)
# dev.off()

>>>>

# Account for cell line aliases and missing histologies
auc_unmatched_na_histologies <- read.delim("./data_munging/pozdeyev2016/auc_unmatched_na_histologies.csv", sep = ",", row.names = 1)
auc_unmatched_na_histologies$accession_id <- NULL
auc_unmatched_na_histologies$Notes <- NULL
auc_unmatched_na_histologies$Histology <- ifelse(auc_unmatched_na_histologies$Histology == "", NA, as.character(auc_unmatched_na_histologies$Histology))
auc_unmatched_na_histologies$CCLE_ccl_name <- ifelse(auc_unmatched_na_histologies$CCLE_ccl_name  == "", NA, as.character(auc_unmatched_na_histologies$CCLE_ccl_name ))
auc_unmatched_na_histologies$Broad_ID <- ifelse(auc_unmatched_na_histologies$Broad_ID == "", NA, as.character(auc_unmatched_na_histologies$Broad_ID))

@@

```{r}
ccle_poz <- read.delim("./data_munging/pozdeyev2016/CCLE_drug_response_metrics.csv.gz", sep = ",")
ccle_poz <- merge(ccl_histologies, ccle_poz, by = "Cell_line", all.y = TRUE)
ccle_poz$InCCLE <- 1
ccle_poz$InCTRP <- 0
ccle_poz$InGDSC <- 0

# ccle_test <- merge(select(ccle_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "CCLE"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)

ctrp_poz <- read.delim("./../htscreens_giant_files/pozdeyev2016/CTRP_drug_response_metrics.csv.gz", sep = ",")
ctrp_poz <- merge(ccl_histologies, ctrp_poz, by = "Cell_line", all.y = TRUE)
ctrp_poz$InCCLE <- 0
ctrp_poz$InCTRP <- 1
ctrp_poz$InGDSC <- 0
# ctrp_test <- merge(select(ctrp_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "CTRP"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)

gdsc_poz <- read.delim("./data_munging/pozdeyev2016/GDSC_drug_response_metrics.csv.gz", sep = ",")
gdsc_poz <- merge(ccl_histologies, gdsc_poz, by = "Cell_line", all.y = TRUE)
gdsc_poz$InCCLE <- 0
gdsc_poz$InCTRP <- 0
gdsc_poz$InGDSC <- 1
# gdsc_test <- merge(select(gdsc_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "GDSC"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)

auc_unmatched <- bind_rows(ccle_poz, ctrp_poz, gdsc_poz)
# auc_unmatched$AUC_EC50 <- as.numeric(as.character(auc_unmatched$AUC_EC50))
auc_unmatched$AUC_IC50 <- as.numeric(as.character(auc_unmatched$AUC_IC50))
# auc_unmatched$sample_ID <- with(auc_unmatched, paste(Database, Cell_line, Histology, sep = "_"))
auc_unmatched$Database_Drug_name <- with(auc_unmatched, paste(Database, Drug_name, sep = "_"))

num_auc_per_db_unmatched <- auc_unmatched %>% count(Database)

@@

# Create merged dataset with sample_ids in the rows and drugs across the columns
auc_unmatched_wide <- dcast(auc_unmatched, Cell_line + Histology + CCLE_ccl_name + Broad_ID + InCCLE + InCTRP + InGDSC ~ Database_Drug_name, value.var = "AUC_IC50", fun.aggregate = mean, fill = 1000000)
auc_unmatched_wide[, 8:ncol(auc_unmatched_wide)] <- auc_unmatched_wide[, 8:ncol(auc_unmatched_wide)] %>% replace_with_na_all(condition = ~.x == 1000000)
# auc_unmatched_wide <- aggregate(. ~ colnames(auc_unmatched_wide)[c(1:4)], data = auc_unmatched_wide, FUN = na.omit, na.action = "na.pass")
# write.csv.gz(auc_unmatched_wide, file = "./data_munging/pozdeyev2016/merged_auc_vCHANGEDATE.3.csv.gz", row.names = FALSE, na = "NA")
```

```{r}

```

@@

Exploratory plots:
```{r, eval=FALSE}
futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
venn_all_ccl_unmatched_pozdeyev <- venn.diagram(list("CCLE" = unique(ccle_poz$Cell_line), "CTRP" = unique(ctrp_poz$Cell_line), "GDSC" = unique(gdsc_poz$Cell_line)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
# png("./gcn_denise/pozdeyev_unmatched/pozdeyev_venn_all_ccl_unmatched.png", res = 500, units = "in", width = 6, height = 6)
# grid.newpage()
# grid.draw(venn_all_ccl_unmatched_pozdeyev)
# dev.off()
